---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## ambientweatheR

`ambientweatheR` provides programmatic access to an Ambient Weather user's weather station data via REST API. 

Ambient Weather API documentation available [HERE](https://ambientweather.docs.apiary.io/#).

Main functions:

- `list_user_devices`: Lists user's available devices and each device's most recent data
- `fetch_device_data`: Fetches data from a device for a given date, or for the last 24 hours

## Installation

```{r eval=FALSE}
devtools::install_github("andrewflack/ambientweatheR")
```

## Example

```{r, message = FALSE}
library(ambientweatheR)
library(tidyverse)
```

```{r}
mac_address <- list_user_devices() %>% pluck("macAddress")
```

```{r, eval = FALSE}
df <- seq.Date(as.Date("2019-08-01"), as.Date("2019-08-04"), "day") %>% 
  map(as.character) %>% 
  map_df(~ fetch_device_data(mac_address, .x))
```

```{r, echo = FALSE}
load(system.file("extdata", "sysdata.rda", package = "ambientweatheR"))
```

```{r}
df %>% 
  select(date_time, tempf, feelsLike) %>% 
  gather(key = "key", value = "value", -date_time) %>% 
  ggplot(aes(x = date_time, y = value, colour = key)) + 
  geom_point()
```

